---
title: "ACC DDMT Event Filter"
output: html_document
date: "2022-07-14"
---

```{r}
pacman::p_load(data.table, tidyverse, dplyr, ggplot2, lubridate,
               janitor, zoo)
```

```{r}
df <- fread("../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/Tracking/DrySeason/DDMT_export/PH_ST_18/Filename_continuous_export_split#1_4.txt") %>% clean_names
# df <- df[,c(1:5,7:11,17:22)]
```

# Find all the 
```{r}
df$datetime <- dmy_hms(paste0(df$date, " ", df$time_hh_mm_ss_ddd))
plot(df$acc_z_sm, col = df$marked_event+1, cex = df$marked_event+0.1)
abline(h = 0.2)
```


# flying
```{r}

f <- df[which(df$acc_z_sm > 0.2),]
```

## plot marked events
```{r}
with(df[200000:300000,], plot(datetime, acc_z, type = "l"))
points(f$datetime[f$marked_event == 1], 
       y = rep(1, length(which(f$marked_event == 1))), 
       col = 2,
       cex = .5)
```

# decide if individual bouts are true foraging events

## what is the distribution of bouts?
```{r}
# run length encoding
r <- rle(f$marked_event)

r$lengths[r$values == 1] %>% hist(breaks = 100)
r$lengths[r$values == 1] %>% summary
```
Looks like most foraging bouts are a single point long, which is too short to include.

What about events that have only a few points between them? Should we include those?
```{r}
r$lengths[r$values == 0] %>% hist(breaks = 5000, xlim = c(0,100))
# length(which(r$values <= 5))
```

Let's fill in the gaps and merge the short breaks
```{r}
r
```

## remove short breaks (<=5 samples) in foraging events
```{r}
i = 5
for(i in 1:length(r$lengths)){
  if(r$values[i] == 0){
    if(r$lengths[i] <= 5){
      # what to do with first and last events?
      try(start <- sum(r$lengths[1:(i-1)])+1)
      if(i == 1) start <- 1
      end <- sum(r$lengths[1:i])
      tt <- f$marked_event[start:end] %>% table
      # relabel events as foraging
      if(tt <= 5){
        f$marked_event[start:end] <- 1
      }
    }
  }
}

```

## rerun run length encoding with fewer short breaks in foraging events
```{r}
r <- rle(f$marked_event)
r$lengths[r$values == 0] %>% hist(breaks = 5000, xlim = c(0,100))
```

## remove short and long foraging events
Let's say that foraging is between half a second to 2 seconds long, so we will filter out everything that is less than 5 and greater than 50 (given 25 Hz sampling rate).

```{r}
i = 1
for(i in 1:length(r$lengths)){
  if(r$values[i] == 1){
    if(r$lengths[i] < 12 | r$lengths[i] > 50){
      # what to do with first and last events?
      start <- {}
      end <- {}
      try(start <- sum(r$lengths[1:(i-1)])+1)
      if(i == 1) start <- 1
      end <- sum(r$lengths[1:i])
      tt <- f$marked_event[start:end] %>% table
      # relabel events as not foraging
      if(tt < 12 | tt > 50){
        f$marked_event[start:end] <- 0
      }
    }
  }
}

```
# recalc rle
```{r}
r <- rle(f$marked_event)
r$lengths[which(r$values == 1)] %>% hist(breaks = 100, xlim = c(0,70))
```

# plot updated marked events
```{r}
with(df[280000:290000,], #[73000:74000,], #[60000:120000,], 
     plot(datetime, acc_z+2, type = "o",
          cex = 0.1,
          ylim = c(-1,5), col = rgb(0,0,0,.5)))
lines(df$datetime, df$ve_dba, cex = .1, col = rgb(0,0.1,1,.5), type = "o")
points(f$datetime[f$marked_event == 1], 
       y = rep(1, length(which(f$marked_event == 1))), 
       col = 2,
       cex = 1)
```
# investigate marked events
```{r}
r$lengths[4]
i = 4
for(i in 41:80){#length(r$lengths)){
  if(r$values[i] == 1){
      start <- {}
      end <- {}
      try(start <- sum(r$lengths[1:(i-1)])+1)
      if(i == 1) start <- 1
      end <- sum(r$lengths[1:i])
      tt <- f$marked_event[start:end] %>% table
      buff <- 20
      
      with(f[(start-buff):(end+buff),], 
           plot(datetime, acc_z, type = "l", 
                main = paste0(f$datetime[start], ", N = ", length(start:end))))
      with(f[(start-buff):(end+buff),], lines(datetime, acc_z_sm, col = 2))
      with(f[(start-buff):(end+buff),], lines(datetime, ve_dba, col = 3))
      with(f[(start-buff):(end+buff),], lines(datetime, ve_dba_smoothed, col = 4))
      abline(v = f$datetime[start], lty = 2)
      abline(v = f$datetime[end], lty = 2)
      legend("topleft", col = c(1:4), 
             legend = c("Z", "Z_sm", "VeDBA", "VeDBA_sm"), 
             lty = 1, cex = .75)
      
      summary(f[start:end,])
    }
  }

```

```{r}
f$n <- lapply(seq_along(1:length(r$lengths)), function(i){
  return(rep(r$lengths[i], r$lengths[i]))
}) %>% unlist
```

# remove events at the beginning and end
These come from the transition to flying but don't represent true pauses



## define a foraging bout
### must have at least 60 seconds between the next foraging bout
### must have a duration over 600 seconds
```{r}
f$difftime <- c(NA, f$datetime %>% diff)

idx <- c(1, which(f$difftime > 60), nrow(f))
i
f$bout <- NA
for(i in 1:(length(idx)-1)){
  f$bout[idx[i]:(idx[i+1]-1)] <- i
}
tt <- f$bout %>% table
f$bout[f$bout %in% which(tt < 600)] <- NA
```

# summarize data
```{r}
f %>% group_by(bout) %>% 
  summarise(length = n(),
            start = min(datetime),
            end = max(datetime),
            visits = length(rle(marked_event)$values==1))
            
f$ve_dba %>% 
```

# get wingbeat
```{r}
localMaxima <- function(x) {
  # Use -Inf instead if x is numeric (non-integer)
  y <- diff(c(-.Machine$integer.max, x)) > 0L
  rle(y)$lengths
  y <- cumsum(rle(y)$lengths)
  y <- y[seq.int(1L, length(y), 2L)]
  if (x[[1]] == x[[2]]) {
    y <- y[-1]
  }
  y
}


```


```{r}
idx <- which(f$bout == 10)
with(f[idx,], plot(datetime, acc_z, type = "l"))
# with(f[idx[1:10],], points(datetime, acc_z))

peaks <- localMaxima(f$acc_z[idx])
diffpeaks <- diff(peaks)
plot(f$datetime[peaks[-1]], diffpeaks)
lines(f$datetime[peaks[-c(1:500, (length(peaks)-499):length(peaks))]], 
      rollmean(as.zoo(diffpeaks), k = 1000), col = 2)

hist(diffpeaks, breaks = 100)
hz <- 1/(mean(diffpeaks)*0.04)
with(f[idx[peaks],], points(datetime, acc_z, col = 2))

length(idx[-1])
length(diffpeaks)
length(f$datetime[peaks[-c(1:499, (length(peaks)-499):length(peaks))]])
length(rollmean(as.zoo(diffpeaks), k = 1000))
```

```{r}
x <- c(1,2,9,9,2,1,1,5,5,1)
localMaxima(x) #
xz <- as.zoo(x)
rollapply(xz, 3, function(x) which.max(x)==2)
```

