---
title: "BORIS_ACC_FC"
output: html_document
date: 2023-08-01
---

Code for Johannes to summarize the behavioral categories of captive Phyllostomus 
hastatus recorded from videos and estimated from acceleration models.

# load libraries
```{r}
library(pacman)
p_load(tidyverse, data.table, lubridate, vcd, reshape2, report)
```

# load data
```{r}
load("../../../../Dropbox/MPI/Dechmann_Lab/Johannes Bernecker/thin_fc_bats.robj")
```


# summarize the number and proportion of behaviors observed for each bat
Use this code as a template for all four individuals
```{r}
idx <- which(heart1s$behavior == "climbing" | heart1s$behavior == "grooming" |
                              heart1s$behavior == "flying" | heart1s$behavior == "sleeping")

heart1s_filter <- heart1s[idx,]

t <- heart1s_filter$behavior %>% table() 
(t/nrow(heart1s_filter)) %>% round(2)

#heart$heart_behav <- predict(heart.rf, newdata = heart)
(table(heart1s_filter$heart_behav)/nrow(heart1s_filter)) %>% round(2)

#heart$moon_behav <- predict(moon.rf, newdata = heart)
(table(heart1s_filter$moon_behav)/nrow(heart1s_filter)) %>% round(2)

#heart$bolt_behav <- predict(bolt.rf, newdata = heart)
(table(heart1s_filter$bolt_behav)/nrow(heart1s_filter)) %>% round(2)

#heart$star_behav <- predict(star.rf, newdata = heart)
(table(heart1s_filter$star_behav)/nrow(heart1s_filter)) %>% round(2)
```
Make a table with four columns (the percentage of each behavior per bat and the total number of rows as the fifth column)


# How well do the models match the observed data
Here we compare the predicted behavior from the four models for each individual. We expect that the model trained on the bat will give the best results.
## heart
```{r}
#heart$heart_behav <- predict(heart.rf, newdata = heart)
df_heart <- as.data.frame(
  rbind(
    (table(heart1s$heart_behav)/nrow(heart1s)) %>% round(2),
    
    #heart$moon_behav <- predict(moon.rf, newdata = heart)
    (table(heart1s$moon_behav)/nrow(heart1s)) %>% round(2),
    
    #heart$bolt_behav <- predict(bolt.rf, newdata = heart)
    (table(heart1s$bolt_behav)/nrow(heart1s)) %>% round(2),
    
    #heart$star_behav <- predict(star.rf, newdata = heart)
    (table(heart1s$star_behav)/nrow(heart1s)) %>% round(2)))

df_heart$model <- c("heart", "moon", "bolt", "star")
df_heart$bat <- "heart"
```


## star
```{r}

df_star <- as.data.frame(
  rbind(
    (table(star1s$heart_behav)/nrow(star1s)) %>% round(2),

    (table(star1s$moon_behav)/nrow(star1s)) %>% round(2),

    (table(star1s$bolt_behav)/nrow(star1s)) %>% round(2),

    (table(star1s$star_behav)/nrow(star1s)) %>% round(2))) 

df_star$model <- c("heart", "moon", "bolt", "star")
df_star$bat <- "star"
```

## moon
```{r}
df_moon <- as.data.frame(
  rbind(
    (table(moon1s$heart_behav)/nrow(moon1s)) %>% round(2),
    
    (table(moon1s$moon_behav)/nrow(moon1s)) %>% round(2),
    
    (table(moon1s$bolt_behav)/nrow(moon1s)) %>% round(2),
    
    (table(moon1s$star_behav)/nrow(moon1s)) %>% round(2)))

df_moon$model <- c("heart", "moon", "bolt", "star")
df_moon$bat <- "moon"
```

## bolt
```{r}
df_bolt <- as.data.frame(
  rbind(
    (table(bolt1s$heart_behav)/nrow(bolt1s)) %>% round(2),
    
    (table(bolt1s$moon_behav)/nrow(bolt1s)) %>% round(2),
    
    (table(bolt1s$bolt_behav)/nrow(bolt1s)) %>% round(2),
    
    (table(bolt1s$star_behav)/nrow(bolt1s)) %>% round(2)))

df_bolt$model <- c("heart", "moon", "bolt", "star")
df_bolt$bat <- "bolt"

```

### plot model similarity
```{r}
df_model <- rbind(df_heart, df_star, df_moon, df_bolt)
df_model_mlt <- reshape2::melt(df_model)

# do models from different bats give similar results?
ggplot(df_model_mlt, aes(x = model, y = value, col = variable, group = variable))+
  geom_line()+
  facet_wrap(~bat)+
  theme_bw()

# how variable are the models?
ggplot(df_model_mlt, aes(x = variable, y = value, col = variable))+
  geom_boxplot()+
  facet_wrap(~bat)+
  theme_bw()
df_model %>% group_by(bat) %>% 
  dplyr::summarise(mean_climbing = mean(climbing))

```

# Statistics for comparing the similarity of predicted behaviors
We need to think about how to define the accuracy of the models and similarity between bats. I think these association stats could work for both, but play around with it and see what you think.

## what is the significance of the behavior match?
### store all signficance tests in a matrix
```{r}
m <- matrix(NA, 4,4)
rownames(m) <- c("heart", "moon", "bolt", "star")
colnames(m) <- c("heart", "moon", "bolt", "star")
m
```

### compare the behaviors observed by the video with behaviors predicted by the moon model
```{r}
# create a contingency table 
t <- with(heart1s_filter, table(behavior, moon_behav))
t

# this calculates association statistics between pairs of bats
a <- assocstats(t)
a

m["heart", "moon"] <- a$contingency
```

Repeat this for each observed behavior vs model behavior combination.


We can do the same analysis for comparing model performance between the heart and moon models
### create a new matrix for significance tests between model performances
```{r}
# model maxtrix
mm <- matrix(NA, 4,4)
rownames(mm) <- c("heart", "moon", "bolt", "star")
colnames(mm) <- c("heart", "moon", "bolt", "star")
mm
```

```{r}
# create a contingency table 
t <- with(heart1s_filter, table(heart_behav, moon_behav))
t

# this calculates association statistics between pairs of bats
a <- assocstats(t)
a

mm["heart", "moon"] <- a$contingency
```

Repeat this for each pair of bats, although no need to do repeated associations, eg. moon vs heart, since we just did heart vs moon.


Ultimately, we are just interested in sleeping, so we could also rerun all of the analysis as sleeping vs not sleeping to evaluate model performance.

# look at behaviors for each day
## summarise behaviors based on the model trained for that bat for each day
### heart
```{r}
heart1s %>% group_by(date = date(time)) %>% 
  dplyr::summarise(flying = length(which(heart_behav == "flying"))/n(),
                   climbing = length(which(heart_behav == "climbing"))/n(),
                   grooming = length(which(heart_behav == "grooming"))/n(),
                   sleeping = length(which(heart_behav == "sleeping"))/n(),
                   ODBA = sum(ODBA, na.rm = TRUE),
                   VeDBA = sum(VeDBA, na.rm = TRUE),
                   count = n()) -> h_sum
h_sum$bat <- "heart"
# remove days where we didn't record the entire day
h_sum <- h_sum[h_sum$count == 86400,]

h_sum_mlt <- reshape2::melt(h_sum, c("bat", "date", "count", "ODBA", "VeDBA"))

ggplot(h_sum_mlt, aes(x = date, y = value*100, col = variable))+
  geom_point()+
  ylab("%")+
  theme_bw()
```
something weird happens around April 12 when climbing becomes super frequent, but sleeping and grooming being the most common behaviors makes sense.
### bolt
```{r}
bolt1s %>% group_by(date = date(time)) %>% 
  dplyr::summarise(flying = length(which(bolt_behav == "flying"))/n(),
                   climbing = length(which(bolt_behav == "climbing"))/n(),
                   grooming = length(which(bolt_behav == "grooming"))/n(),
                   sleeping = length(which(bolt_behav == "sleeping"))/n(),
                   ODBA = sum(ODBA, na.rm = TRUE),
                   VeDBA = sum(VeDBA, na.rm = TRUE),
                   count = n()) -> b_sum
b_sum$bat <- "bolt"
b_sum <- b_sum[b_sum$count == 86400,]

b_sum_mlt <- reshape2::melt(b_sum, c("bat", "date", "count", "ODBA", "VeDBA"))

ggplot(b_sum_mlt, aes(x = date, y = value*100, col = variable))+
  geom_point()+
  ylab("%")+
  theme_bw()
```
missing recordings on April 8th
### moon
```{r}
moon1s %>% group_by(date = date(time)) %>% 
  dplyr::summarise(flying = length(which(moon_behav == "flying"))/n(),
                   climbing = length(which(moon_behav == "climbing"))/n(),
                   grooming = length(which(moon_behav == "grooming"))/n(),
                   sleeping = length(which(moon_behav == "sleeping"))/n(),
                   ODBA = sum(ODBA, na.rm = TRUE),
                   VeDBA = sum(VeDBA, na.rm = TRUE),
                   count = n()) -> m_sum
m_sum$bat <- "moon"
m_sum <- m_sum[m_sum$count == 86400,]

m_sum_mlt <- reshape2::melt(m_sum, c("bat", "date", "count", "ODBA", "VeDBA"))

ggplot(m_sum_mlt, aes(x = date, y = value*100, col = variable))+
  geom_point()+
  ylab("%")+
  theme_bw()
```

### star
```{r}
star1s %>% group_by(date = date(time)) %>% 
  dplyr::summarise(flying = length(which(star_behav == "flying"))/n(),
                   climbing = length(which(star_behav == "climbing"))/n(),
                   grooming = length(which(star_behav == "grooming"))/n(),
                   sleeping = length(which(star_behav == "sleeping"))/n(),
                   ODBA = sum(ODBA, na.rm = TRUE),
                   VeDBA = sum(VeDBA, na.rm = TRUE),
                   count = n()) -> s_sum
s_sum$bat <- "star"
s_sum <- s_sum[s_sum$count == 86400,]

s_sum_mlt <- reshape2::melt(s_sum, c("bat", "date", "count", "ODBA", "VeDBA"))

ggplot(s_sum_mlt, aes(x = date, y = value*100, col = variable))+
  geom_point()+
  ylab("%")+
  theme_bw()
```

### all bats
```{r}
bat_sum_mlt <- rbind(h_sum_mlt, m_sum_mlt, b_sum_mlt, s_sum_mlt)
ggplot(bat_sum_mlt, aes(x = date, y = value*100, col = variable))+
  geom_point()+
  ylab("%")+
  theme_bw()+facet_wrap(~bat)
```

# how does ODBA and VeDBA correlate with total sleep?
## all bats
```{r}
ggplot(bat_sum_mlt, aes(x = value, y = VeDBA, col = bat, group = variable))+
  geom_point()+geom_smooth(method = "lm")+
  facet_wrap(~variable, scales = "free")

ggplot(bat_sum_mlt, aes(x = value, y = ODBA, col = bat, group = variable))+
  geom_point()+geom_smooth(method = "lm")+
  facet_wrap(~variable, scales = "free")
```

# What relationships would you have expected for ODBA and VeDBA to have with each behavior?
Climbing and flying should create higher VeDBA, so an increase in that alone would shoud have a positive relationship. Why don't we see that relationship? Sleeping means you aren't moving at all, so, in isolation, more sleep should mean lower VeDBA. 

# model these results
```{r}
bat_sum_mlt
bat_sum <- rbind(h_sum, m_sum, b_sum, s_sum)

fit_sleeping <- lm(VeDBA ~ sleeping, data = bat_sum)
summary(fit_sleeping)
report(fit_sleeping) %>% as.data.frame()

fit_grooming <- lm(VeDBA ~ grooming, data = bat_sum)
summary(fit_grooming)
report(fit_grooming) %>% as.data.frame()

# copy this code for flying and climbing
```



