---
title: "BORIS_Video"
output: html_document
---

# load libraries
```{r}
# install.packages("pacman")
library(pacman)
p_load(lubridate, # date time function 
       data.table, # easier for extreme 
       tidyverse, 
       dplyr, 
       vcd, # assocation statistics
       install = TRUE # accelerometer - summarizing accelerometer data
       )
```


## load video annotations and plot bat behaviors
```{r}
# change to the path to your exported files
path <- "../../../../Dropbox/MPI/Dechmann_Lab/Johannes Bernecker/boris_files/ExportedData/updated/"
files <- list.files(path, pattern = ".csv")

video_data <- data.frame()

i = 1

for(i in 1:length(files)){
  a <- data.table::fread(paste0(path, files[i]), header = TRUE)
  # which bats are active?
  paste0(a$Behavior, a$Subject) %>% table
  
  a <- a[order(a$Subject, a$Behavior, a$Time),]
  
  a_mlt <- data.frame(start = a$Time[a$Status == "START"],
                            stop = a$Time[a$Status == "STOP"],
                            behavior = a$Behavior[a$Status == "START"],
                            subject = a$Subject[a$Status == "START"])
  a_mlt$duration <- a_mlt$stop - a_mlt$start
  a_mlt$file <- files[i]
  
  p <- ggplot(a_mlt, aes(x = start, xend = stop, y = behavior, yend = behavior, 
                          col = behavior, group = subject))+
    geom_segment(size = 2)+facet_wrap(~subject)+ggtitle(files[i])
  print(p)
  
  video_data <- rbind(video_data, a_mlt)
}


```
Looks good! I don't think there are any overlapping files


## summarise behaviors in videos
```{r}
video_data %>% group_by(behavior, subject, file) %>% summarise(total_duration = sum(duration)) -> video_data_sum

ggplot(video_data_sum, aes(x = behavior %>% factor, y = total_duration, col = subject))+
  geom_point()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  facet_wrap(~file)

```

# Here are some ideas for data analysis: 
## Do bats sleep more or less in groups?

Check videos to see which bats are associated with each other
```{r}

group_bats <- c("heart", "moon", "star")
solo_bat <- "bolt"


```



##  How synchronized are their behaviors?
```{r}
behavior_sync <- function(file, bat1, bat2){
  b1 <- video_data[which(video_data$file == file & video_data$subject == bat1),]
  b2 <- video_data[which(video_data$file == file & video_data$subject == bat2),]

  # expand the data into behaviors for each individual for each frame
  b1_full <- data.frame()  
  k = 1
  for(k in 1:nrow(b1)){
    temp <- data.frame(time = seq(b1$start[k], b1$stop[k], by = 1/50),
                       subject = b1$subject[k],
                       behavior = b1$behavior[k])
    b1_full <- rbind(b1_full, temp)
  }
  
  b2_full <- data.frame()  
  k = 1
  for(k in 1:nrow(b2)){
    temp <- data.frame(time = seq(b2$start[k], b2$stop[k], by = 1/50),
                       subject = b2$subject[k],
                       behavior = b2$behavior[k])
    b2_full <- rbind(b2_full, temp)
  }
  
  b1_full <- b1_full[order(b1_full$time),]
  # duplicated(b1_full$time)
  
  b2_full <- b2_full[order(b2_full$time),]
  
  b1_b2 <- left_join(b1_full, b2_full, "time")
  
  b1_b2$behavior.x.num <- b1_b2$behavior.x %>% factor(levels = c(unique(video_data_sum$behavior))) %>% as.numeric()
  b1_b2$behavior.y.num <- b1_b2$behavior.y %>% factor(levels = c(unique(video_data_sum$behavior))) %>% as.numeric()
  
  summary(b1_b2)
  
  # cross correlation function will tell us at what lag and how strongly correlated the behaviors are for a pair of individuals
  b1_b2 <- na.omit(b1_b2)
  return(b1_b2)
  
  p <- ggplot(b1_b2)+
    geom_point(aes(time, behavior.x), size = 3)+
    geom_point(aes(time, behavior.y), col = 2)
  print(p)
  
  c <- ccf(b1_b2$behavior.x.num, b1_b2$behavior.y.num, lag = 1000)
  
  # time lag between individuals
  print(paste0("Time lag ", c$lag[c$acf %>% which.max]/50, " sec"))
  
}

```

You can iteratively compare pairs of bats in each file
```{r}
files <- unique(video_data$file)
bats <- unique(video_data$subject)

# here we are comparing bats 1 and 3 in file 1
sync1 <- behavior_sync(files[1], bat1 = bats[1], bats[3])

sync1$behavior.x.num %>% unique
sync1$behavior.y.num %>% unique

# index out of frame behaviors and remove them
idx <- which(sync1$behavior.x.num == 8 | sync1$behavior.y.num == 8)

ifelse(length(idx) > 0, sync_in_frame <- sync1[-idx,], sync_in_frame <- sync1)

p <- ggplot(sync_in_frame)+
  geom_point(aes(time, behavior.x), size = 3)+
  geom_point(aes(time, behavior.y), col = 2)
print(p)

# what is the significance of the behavior match?
t <- table(sync_in_frame$behavior.x, sync_in_frame$behavior.y)

# this calculates association statistics between pairs of bats
a <- assocstats(t)

```


You can then compare if these assocations are consistent across videos, time of day, etc.

