---
title: "FPT Foraging Sites"
output: html_document
---

Exploring FPT to identify foraging sites

HMM didn't work well when attempting to regularize the data

# load libraries
```{r}
library(pacman)

p_load(momentuHMM, lubridate, data.table, zoo, move, dplyr, adehabitatLT, mixtools, ggplot2, latticeExtra, janitor, archdata, sp, leaflet, rgdal, rgeos, spatstat, rworldmap, 
       ggmap, gstat, leaflet, mapview, raster, rnaturalearth, rnaturalearthdata, marmap)

# source("../../../movebank_login.R")

proj.ll <- CRS('+proj=lonlat +datum=WGS84 +no_defs')
projUTM <- CRS("+proj=utm +zone=17 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")
```

# load data
```{r}
load("../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/results_part1.rdata")
load("../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/phastmove.rdata")
# inf <- read.delim("../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/Greater spear-nosed bat (Phyllostomus hastatus) in Bocas del Toro 2021-2022-reference-data.csv", header=T, sep=',', as.is=T)
```

## load maps
```{r}
panama <- ne_countries(country = "Panama", scale = 10)
panama <- ne_states(country = "Panama", returnclass = "sf")
bocas <- panama[panama$name == "Bocas del Toro",]
```



```{r}
# str_name<-'../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/NaturalEarthData/GRAY_HR_SR_OB_DR.tif' 
# world=raster(str_name)
# 
# Bocas <- crop(world, extent(bocas))
# 
# plot(Bocas)
# 
# world_spdf <- as(world, "SpatialPixelsDataFrame")
# world_df <- as.data.frame(world_spdf)
# colnames(world_df) <- c("value", "x", "y")
# 
# ggplot(data = bocas) +
#     geom_sf() 
```

# get technosmart data
```{r}
technosmart <- "F:/TrackingDryseason/"
gps_files <- list.files(path = technosmart, pattern = "*gps.csv", full.names = TRUE, recursive = TRUE)

aj <- data.table()
for(i in 1:length(gps_files)){
  aj_tag <- fread(gps_files[i]) %>% clean_names() 
  aj <- rbind(aj, aj_tag, fill = TRUE)
}


aj$time <- aj$timestamp %>% dmy_hms

plot(aj$location_lon, aj$location_lat, asp = 1, col = as.factor(aj$tag_id))
```


```{r}
aj$battery_v %>% plot
```
# merge technosmart and vesper tracks
```{r}
move.df$location_lon <- move.df$location_long
names(aj[,c(1,7,8,3,4,2)])
names(move.df[,c(1,13, 55, 25, 26, 17)])
a <- aj[,c(1,7,8,3,4,2)] %>% as.data.table()
a$timestamp <- dmy_hms(a$timestamp)
b <- move.df[,c(1,13, 55, 25, 26, 17)]
df <- rbind(a,b)
```


# Create traj  
```{r}
# plot(phast)
# phast <- phast[phast$location_lon > -90,]
# df <- as.data.frame(phast)

# df <- aj
# df$location_lat <-  df$location.lat
# df$location_lon <- df$location.lon


po <- spTransform(SpatialPoints(df[,c("location_lon", "location_lat")], proj4string=proj.ll), CRSobj=projUTM)
df$y <- po@coords[,2]
df$x <- po@coords[,1]

df$date <- date(df$time)
df$ID <- paste0(df$tag_id, "_", df$date)

p.traj <- as.ltraj(data.frame(X = df$x, Y = df$y), date = df$time, id = factor(df$tag_id), burst = df$ID)
pj <- ld(p.traj)

```


# load Bocas
```{r}
m <- brick("../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/Bocas.tif")
m_crop <- crop(m, extent(po))

plotRGB(m_crop,
        r = 3, g = 2, b = 1,
        stretch = "lin",
        axes = TRUE,
        main = "RGB composite image\n Planet Bands 3,2,1")
points(df$x, df$y, col = as.factor(df$ID))


plot(df$x, df$y, col = as.factor(df$ID))
```


## crop raster to changuinola, isla colon, and Isla Cristobal
## crop raster to foraging sites
```{r}

chang_ext <- extent(310809, 354875, 1028174, 1058001)
crist_ext <- extent(351042, 363248, 1015500, 1028174)
colon_ext <- extent(353000, 369000, 1028174, 1058001)

m_chang <- crop(m, chang_ext)
m_crist <- crop(m, crist_ext)
m_colon <- crop(m, colon_ext)

plotRGB(m_crist,
        r = 3, g = 2, b = 1,
        stretch = "lin",
        axes = TRUE,
        main = "RGB composite image\n Planet Bands 3,2,1")
```

# First Passage Time

```{r}
# Determine Optimal Radius
radii <- seq(5, 300, by = 5)
fpts <- fpt(p.traj, radii, units = "seconds")

varfpt <- varlogfpt(fpts, graph = F)
names(varfpt) <- radii

Radius <- as.numeric(names(which.max(colMeans(as.matrix(varfpt), na.rm = TRUE))))

```


### plot radius
```{r}
boxplot(varfpt, ylab = 'Variance of log(FPT)', xlab = 'Radius (m)', main = paste0("Radius = ", Radius, " m"))
abline(v = which(radii == Radius), col = 2)
```


```{r}
fpt_mean <- colMeans(as.matrix(varfpt), na.rm = TRUE)
fpt_se <- {}
for(i in 1:ncol(varfpt)){
  fpt_se[i] <- sd(varfpt[,i], na.rm = TRUE)# /sqrt(length(na.omit(varfpt[,i])))
}
fpt_rad <- data.frame(fpt_mean, fpt_se, radii)
```

### plot fpt radius
```{r}
p <- ggplot(fpt_rad, aes(x = radii, y = fpt_mean))+geom_line()+ 
  geom_errorbar(aes(ymin=fpt_mean-fpt_se, ymax=fpt_mean+fpt_se), width=30, colour = "black") + 
  geom_line() + theme_classic() + xlab("FPT Radius (m)") + ylab("Mean variance (SD)") +
  geom_segment(aes(x = 0, y = max(colMeans(as.matrix(varfpt), na.rm = TRUE)), xend = Radius, yend = max(colMeans(as.matrix(varfpt), na.rm = TRUE))), linetype = "dashed") +
  geom_segment(aes(x = Radius, y = 0, xend = Radius, yend = max(colMeans(as.matrix(varfpt), na.rm = TRUE))), linetype = "dashed") +
  scale_x_continuous(expand = c(0,0)) + scale_y_continuous(expand = c(0,0)) 
p + theme(plot.margin = unit(c(1,1,1,1), "cm"))
# ggpubr::ggarrange(p + theme(plot.margin = unit(c(1,1,1,1), "cm")), labels = "A")
```

### Determine threshold
```{r}
fpt <- unlist(fpt(p.traj, Radius, units = "seconds"))
logfpts <- na.omit(log(fpt))
mixmdl <- mixtools::normalmixEM(logfpts, k = 3)
plot(mixmdl,which=2)
lines(density(logfpts), lty=2, lwd=2)
abline(v = mixmdl$mu)
idx <- 2#which.min(mixmdl$mu)
#2.58 99% CI
#1.96 95% CI

threshold <- mixmdl$mu[idx]+1.96*mixmdl$sigma[idx]
abline(v = threshold, col = 2, lwd = 2, lty = 2)
exp(threshold)
```

### Match FPT data
```{r}
Bats <- {}
for(i in 1:length(p.traj)){
  # layout(cbind(c(1,2), c(3,4), c(5,6)))
  bat <- ld(p.traj[i])
  bat$bat <- burst(p.traj[i])
  fpts <- unlist(fpt(p.traj[i], Radius))
  bat$FPT <- fpts
  bat$FPT01 <- as.numeric(fpts > exp(threshold))
  Bats <- rbind(Bats, bat)
}

Split <- strsplit(as.character(Bats$bat), "_", fixed = TRUE)
Bats$id <- sapply(Split, "[", 1)

summary(Bats)

```
# plot tracks
make pdf


```{r}

IDs <- unique(Bats$burst)
i = 14
pdf(file = "../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Plots/technosmart_tracks_simple.pdf")
for(i in 1:length(IDs)){
  b <- Bats[which(Bats$burst == IDs[i]),]
  # plot(b$x, b$y, col = b$FPT01+1,
  #      asp = 1)

  p <- ggplot(b, aes(x, y, col = log(FPT)))+geom_path()+
    geom_point(aes(size = FPT), shape = 21)+ ggtitle(IDs[i])+
    viridis::scale_color_viridis()+theme_minimal()+
    ylim(c(min(Bats$y),max(Bats$y)))+
    xlim(c(min(Bats$x),max(Bats$x)))
  print(p)

  # ggplot(b[30:100,], aes(x,y,col = FPT))+geom_tile

}
dev.off()


```

```{r}
# use near infrared instead of red
  plotRGB(m_colon,
        r = 4, g = 2, b = 1,
        stretch = "lin",
        axes = TRUE,
        main = IDs[i])
```

### plot tracks with basemap raster
```{r}

# IDs <- unique(Bats$burst)
# i = 1
# pdf(file = "../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Plots/technosmart_tracks_simple.pdf")
# for(i in 1:length(IDs)){
#   b <- Bats[which(Bats$burst == IDs[i]),]
#   # plot(b$x, b$y, col = b$FPT01+1,
#   #      asp = 1)
#   pb <- SpatialPoints(b[,c("x", "y")], proj4string=projUTM)
#   plot(pb)
#   m_bat <- crop(m, extent(pb))
#   
#   plotRGB(m_crop,
#         r = 3, g = 2, b = 1,
#         stretch = "lin",
#         axes = TRUE,
#         main = IDs[i])
#   points(b$x, b$y, type = "o", col = rgb(1,0,0,.2))
# 
#   # ggplot(b[30:100,], aes(x,y,col = FPT))+geom_tile
# 
# }
# dev.off()

```

# Hist FPT
```{r}

Bats$FPT %>% hist(breaks = 500, xlim = c(0,1000))

```
# rasterize FPT
```{r}
###############################
# rasterize points
###############################
## Ilsa San Cristobal

high_fpt <- Bats[which(Bats$FPT > 100),]

r <- raster(ncols=2000, nrows=2000)
r <- projectExtent(r, projUTM)
extent(r) <- chang_ext
# extent(r) <- extent(min(high_fpt$x, na.rm = TRUE)-500, 
#                     max(high_fpt$x, na.rm = TRUE)+500, 
#                     min(high_fpt$y, na.rm = TRUE)-500, 
#                     max(high_fpt$y, na.rm = TRUE)+500)
xy <- cbind(high_fpt$x, high_fpt$y)
r
fpt <- rasterize(xy, r, high_fpt$FPT, fun=sum)
plot(fpt)
FPT <- projectRaster(fpt, crs = proj.ll)
plot(FPT)
values(FPT) <- log(values(FPT))
```


```{r}

spplot(FPT)
fpt_contour <- rasterToContour(FPT, nlevels = 5)

names(df)
p_spat <-  SpatialPointsDataFrame(coords = df[,c("location_lon", "location_lat")], 
                                  data = df,
                                  #data = df[,c(1,7,9,11:15,17,30,40)], 
                                   proj4string = proj.ll)
# p39 <- SpatialPointsDataFrame(coords = df[df$ID == "PH_TS_039_S2_2022-03-15",
#                                           c("location_lon", "location_lat")], 
#                                   data = df[df$ID == "PH_TS_039_S2_2022-03-15",],
#                                   #data = df[,c(1,7,9,11:15,17,30,40)], 
#                                    proj4string = proj.ll)


```

```{r}

m2 <- mapview(p_spat, alpha.regions = 0.1, color = "red")
# m39 <- mapview(p39, alpha.regions = 0.1)
m3 <- mapview(FPT, alpha.regions = 0.50, na.color = "transparent")
m4 <- mapview(fpt_contour, lwd = 0.5, color = "gray40")
m2+m3

```



```{r}
values(FPT) %>% hist

idx <- which(values(FPT) > 10)
xy <- coordinates(FPT)[idx,] %>% unique
lon_bouts <-  SpatialPointsDataFrame(coords = xy, 
                                      data = as.data.frame(xy),
                                   proj4string = proj.ll)
m5 <- mapview(lon_bouts, color = "red", alpha.regions = 0.2)
m5
```

