---
title: "Import Movebank"
output: html_document
---

Here is my initial exploration of the Phyllostomus hastatus tracking data from 2022 in Bocas del Toro Panama.

At this time of the year, it is the dry season and bats are foraging on Balsa flowers. We will see if its possible to extract better variables to look at possible foraging trees but for now we can see if bats simply choose to go to areas with high forest cover compared with secondary forests or agricultural land.

Additionally, we will set up a pipeline to extract flight parameters from each individual as well as run an HMM to define foraging and commuting.

# load libaries
```{r setup, include=FALSE}
library(pacman)
# devtools::install_github("ABoVE-AotM/above")
p_load(above, move, maptools,
       dplyr, leaflet, lubridate, maps, mapdata, marcher, rgdal, 
       gfcanalysis,snow,patchwork,
       raster,rlist,PBSmapping, 
       rnaturalearth, rnaturalearthdata, sp, momentuHMM,
       tidyverse, magrittr, osmdata)

source("../../../movebank_login.R")

proj.ll <- CRS('+proj=longlat +datum=WGS84 +no_defs')
```

```{r}
# fractional tree cover
data_folder <- '../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data'

# aoi <- readOGR(system.file('extdata', package='gfcanalysis'), 'ZOI_NAK_2012')

x <- c(-82.59858974938628,-82.03210720544097, -82.03210720544097,-82.59858974938628)
y <- c(9.125631468384787,9.125631468384787,9.510498999474096,9.510498999474096)
xy <- cbind(x,y)
p <- Polygon(xy)
ps <- Polygons(list(p),1)
sps <- SpatialPolygons(list(ps))
# plot(sps)
proj4string(sps) = CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

aoi <- sps

# # Calculate the google server URLs for the tiles needed to cover the AOI
# tiles <- calc_gfc_tiles(aoi)
# 
# # Check to see if these tiles are already present locally, and download them if 
# # they are not.
# download_tiles(tiles, data_folder, )
# 
# # Extract the GFC data for this AOI from the downloaded GFC tiles, mosaicing 
# # multiple tiles as necessary (if needed to cover the AOI), and saving  the 
# # output data to a GeoTIFF (can also save in ENVI format, Erdas format, etc.).
# gfc_data <- extract_gfc(aoi, data_folder, filename='gfc_Bocas_extract.tif', overwrite = TRUE)
# 
# plot(gfc_data)
# 
# tgfc <- threshold_gfc(gfc_data)
# 
# gfc_stack <- annual_stack(tgfc)
# 
# plot(gfc_stack[[16]])
# 
# save(gfc_data, gfc_stack, tgfc, file = "../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/forestcoverBocas.rdata")
load("../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/forestcoverBocas.rdata")
```


# read movebank data
```{r}
# phast <- getMovebankData(study="Greater spear-nosed bat (Phyllostomus hastatus) in Bocas del Toro 2021-2022", login=login, removeDuplicatedTimestamps = TRUE)
# sensors <- getMovebankSensorsAttributes(study="Greater spear-nosed bat (Phyllostomus hastatus) in Bocas del Toro 2021-2022", login=login)
# 
# save(phast, sensors, file = "../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/phastmove.rdata")
load("../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/phastmove.rdata")
#phast_gps <- getMovebankData(study="Greater spear-nosed bat (Phyllostomus hastatus) in Bocas del Toro 2021-2022", login=login, removeDuplicatedTimestamps = TRUE, sensorID = "GPS")
```

```{r}
phast[[1]] %>% as.data.frame
```

# remove outlier
```{r}
phast <- phast[phast$location_long > -90,]
plot(phast)
```
## add UTM
```{r}
projUTM <- "+proj=utm +zone=17 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
BocasProj <- spTransform(phast, CRSobj=projUTM)

phast$x <- BocasProj$location_long
phast$y <- BocasProj$location_lat
```


```{r}
summary(phast)
sensors
namesIndiv(phast)
move.df <- as.data.frame(phast)
```
# number of individuals
```{r}
length(unique(move.df$tag_id))
sort(table(move.df$local_identifier))
```

# spatial extent of the study
```{r}
range(move.df$location_long)
range(move.df$location_lat)
xlim <- c(-83, -82.2)
ylim <- c(9.3, 9.7)
```
# plot data with tree cover
```{r}
gfc_data 
tree <- crop(gfc_data[[1]], extent(c(xlim, ylim)))

tree.df <- data.frame(x=coordinates(tree)[,1], y=coordinates(tree)[,2], fcover=values(tree))

ggplot(move.df, aes(x=location_long, y=location_lat)) +
  geom_raster(data=tree.df, aes(x=x, y=y, fill=fcover)) +
  scale_fill_viridis_c(name='Fractional tree cover', limits=c(0,100), option='E', alpha=0.7) +
  geom_point(aes(colour=factor(tag_id)), size=0.5, show.legend=F)+ 
  scale_colour_viridis_d(name='Individual', option='A') +
  theme(legend.position='bottom') + coord_equal() +
  labs(x='Longitude', y='Latitude')
```
# clean up excess rasters
```{r}
rm(tree.df, gfc_data, gfc_stack,tgfc); gc()
```

# plot speed
```{r}
ggplot(move.df, aes(x=ground_speed)) +
  geom_histogram(fill='black', colour='black', binwidth=2)+xlim(c(-5,60))

# move.df$speed <- phast %>% speed %>% unlist
plot(move::speed(phast[[1]]))
phast %>% speed %>% unlist %>% hist(breaks = 100)

phast %>% distance %>% unlist %>% hist(breaks = 50000, xlim = c(0,5000))
```
# compare forest cover use between speeds
```{r}
p <- SpatialPoints(move.df[,c('location_long', 'location_lat')], proj4string=CRS('+proj=longlat +datum=WGS84'))

move.df$fcover <- extract(tree, p) # using nearest-neighbour method

ggplot(move.df, aes(x=fcover)) +
  geom_histogram(fill='white', colour='black', binwidth=5) +
  facet_wrap(~factor(ground_speed>2, labels=c('Ground speed < 2m/s', 'Ground speed > 2m/s')), ncol=1)
```
# Adding sun angle and solar time
```{r}
# compute time relative to solar noon for each location
move.df$solar.time <- unlist(lapply(1:nrow(move.df), function(j){
  noon <- solarnoon(p[j,], move.df$timestamp[j], POSIXct.out=TRUE)$time
  tod <- as.numeric(difftime(move.df$timestamp[j], noon, units='hours'))
  return(tod)
}))

# shift solar time to be all-positive, from noon to noon
move.df$solar.time <- (move.df$solar.time+24)%%24

# compute solar elevation
move.df$solar.pos <- unlist(lapply(1:nrow(move.df), function(j){
  pos <- solarpos(p[j,], move.df$timestamp[j])
  return(pos[,2])
}))


twilight <- data.frame('name'= c('Dawn/Dusk', 'Civil Twilight', 'Nautical Twilight', 'Astronomical Twilight'),
                       'solar.pos'=c(0, -6, -12, -18), stringsAsFactors=F)
twilight$name <- factor(twilight$name, levels=c('Dawn/Dusk', 'Civil Twilight', 'Nautical Twilight', 'Astronomical Twilight'))

ggplot(move.df, aes(x=solar.pos)) + 
  geom_histogram(fill='white', colour='black', binwidth=3) +
  geom_vline(data=twilight, aes(xintercept=solar.pos, colour=name), size=1.5) +
  scale_colour_viridis_d(name='', direction=-1)
```

# no sampling during daytime
```{r}
p1 <- ggplot(move.df, aes(x=solar.time)) + geom_histogram(fill='white', colour='black', binwidth=1) + 
  scale_x_continuous(breaks=seq(0,23,2), limits=c(0,23)) +
  theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
p2 <- ggplot(move.df, aes(x=ground_speed)) +
  scale_x_continuous(breaks=seq(0,25,5)) +
  geom_histogram(fill='white', colour='black', binwidth=1.5) + 
  coord_flip() + theme(axis.text.y=element_blank(), axis.title.y=element_blank(), 
                       axis.ticks.y=element_blank(), axis.text.x=element_text(angle=90))
p3 <- ggplot(move.df, aes(x=solar.time, y=ground_speed, colour=fcover)) +
  geom_point(size=0.7) + scale_colour_viridis_c() + 
  scale_x_continuous(breaks=seq(0,23,2), limits=c(0,23)) +
  scale_y_continuous(breaks=seq(0,25,5)) + theme(legend.position='bottom')

p1 + plot_spacer() + p3 + p2 + plot_layout(ncol=2, widths=c(0.8, 0.2), heights=c(0.3, 0.7))
```

# when do bats fly out from the roost?
```{r}
move.df <- ddply(move.df, 'tag_id', function(tmp){
  tmp$day <- c(0, cumsum(diff(tmp$solar.time)<0)) + 1
  tmp <- ddply(tmp, 'day', function(x){
    loc <- c('location_long', 'location_lat')
    x$d2start <- distGeo(x[1,loc], x[,loc])
    return(x)
  })
  return(tmp)
})

# individuals were tracked up to 14 days
# most days display the nice sequence of outbound movement, a stationary phase, and inward movement back to the colony
# there is quite some variation though, and individuals don't always return to the colony while the tags are active
ggplot(move.df, aes(x=solar.time, y=d2start/1000)) +
  geom_path(aes(colour=factor(day))) + scale_colour_viridis_d() +
  facet_wrap(~tag_id, scale='free_y')
```
Additionally, we can see when individuals leave/return to the day roost using a spatial overlay with the boundaries of the bat forest (and the national park as well). I found that openstreetmap has an existing feature for the Kasanka bat forest that looks roughly like the outline presented in the Byng et al. (2010) paper that Roland sent around. If you have anything better, that can easily replaced, but for the point of making progress I’ll use the osm data here. I’ll also make a custom equidistant projection that’s centered on the centroid of the day roost (i.e. distances to the day roost are accurate) because the function expects that locations are in some form of metric projection, rather than longlat.

# get shape file of the island
## figure out how to separate polygons
```{r}
la_gruta <- data.frame(y= 9.395782122798584, x = -82.27111745181531)

panama <- ne_countries(scale = 10, country = "panama", returnclass = "sf")
plot(panama)
ggplot(panama)+geom_sf(fill = "white")+
  coord_sf(xlim = c(-83, -82), ylim = c(9, 9.5))+
  geom_point(data = la_gruta, aes(x,y), col = 2)
  
panama %>% str

panama <- ne_states(country = "panama", returnclass = "sf")
bocas <- filter(panama, name == "Bocas del Toro")
ggplot(bocas)+geom_sf(fill = "white")+
  geom_point(data = la_gruta, aes(x,y), col = 2)
islands <- st_cast(bocas, "POLYGON")
islands[1] %>% str
islands$name <- 1:4
colon <- filter(islands, name == 3)
plot(colon)

# first, let's get hold of the park boundaries
isla_colon <- opq('Isla Colón, Panama') %>%
  add_osm_feature(key = 'natural', value = 'woods') %>% 
  osmdata_sp()
isla_colon
#<- isla_colon$osm_polygons
plot(isla_colon$osm_polygons)


available_features()
```

```{r}
isla_colon <- isla_colon$osm_multipolygons

# download polygon data for the bat forest
forest <- opq(bbox=as.vector(bbox(isla_colon))) %>%
    add_osm_feature(key='name', value='Forest', value_exact=F) %>%
    osmdata_sp()  
forest <- forest$osm_multipolygons

plot(isla_colon)
plot(forest, add=T, col='forestgreen')
```


The regularisation is required as, while the tags were programmed to sample locations regularly, there are inconsistencies in the sampling scheme. This is not necessarily an issue, but could cause problems for the second-stage model to annotate behaviour and derive empirical distributions for the different modes of movement. The sampling inconsistencies in this data set are (apart from the obvious gaps during the GPS sleep time) relatively minor, which is why I think we can attempt the regularisation for each individual-day trajectory by fitting continuous-time correlated random walk models using the crawl package.

Following regularisation, I will fit Hidden Markov Models (using the momentuHMM package) to identify different modes of movement behaviour from the trajectories (I’m expecting to see resting/area-restricted movement, slow, undirected, and fast, directed movement to show up here). We can also include environmental and other covariates to the model, such as time of day, or theoretically forest cover. The resulting model will provide us with a behavioural annotation of the trajectories as well with ML estimates of the probability distribution parameters we choose to describe the movement (e.g. step length and turning angle). We should also be able to simulate new trajectories from this model.

The second step of the initial analyses will be to identify foraging sites. My plan here is to make use of the revisitation analyses provided by the recurse package, which calculates revisitations to animal relocations along a single or multiple trajectories (or even user-specified locations/polygons - such as the day roost). My thinking here is that applying the analysis to individual trajectories (or just the stationary relocations, identified using the Hidden Markov Model) should highlight sites where individuals spent considerable time. We’ll have to make the assumption that these sites were used by the individuals for foraging.

```{r}
save(move.df, phast, tree, proj.ll, file = "../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/results_part1.rdata")
```
















# acc data is strange for vesper bats
```{r}
phast$acceleration_raw_x %>% plot
acc_idx <- which(!is.na(phast$acceleration_raw_x))
phast[acc_idx,] %>% plot
summary(phast[acc_idx,])
```


```{r}
layout(c(1,2,3))
plot(phast$acceleration_raw_x[acc_idx], type = "l")
plot(phast$acceleration_raw_y[acc_idx], type = "l")
plot(phast$acceleration_raw_z[acc_idx], type = "l")
```

```{r}



```



```{r}
p_sum <- data.frame()
j = 1
for(j in 1:length(unique(phast$tag_id))){
  indiv <- phast[[j]]
  plot(indiv)
  scan_track(x = indiv$location_long, y = indiv$location_lat, time = indiv$timestamp, 
             cex = indiv$ground_speed*2/max(indiv$ground_speed))  
  
  # identify number of foraging days
  dates <- indiv$timestamp %>% ymd_hms %>% date %>% unique 
  dates
  
  # departure, return, duration of flights
  ind_sum <- data.frame(tag_id = indiv$tag_id[1], date = dates, 
                        start = ymd_hms("2000-01-01 00:00:00"), 
                        end = ymd_hms("2000-01-01 00:00:00"))

  for(i in 1:length(dates)){
    d <- indiv[date(indiv$timestamp) == dates[i],]
    plot(d)
    ind_sum$start[i] <- d$timestamp[1]
    ind_sum$end[i] <- d$timestamp[nrow(d)]
    ind_sum$distance[i] <- sum(distance(d))
    
    ind_sum$max_speed[i] <- max(speed(d))
  }
  p_sum <- rbind(p_sum, ind_sum)
}

```


# identify foraging locations

## HMM
```{r}

```


