---
title: "Import Movebank"
output: html_document
---

Here is my initial exploration of the Phyllostomus hastatus tracking data from 2022 in Bocas del Toro Panama.

At this time of the year, it is the dry season and bats are foraging on Balsa flowers. We will see if its possible to extract better variables to look at possible foraging trees but for now we can see if bats simply choose to go to areas with high forest cover compared with secondary forests or agricultural land.

Additionally, we will set up a pipeline to extract flight parameters from each individual as well as run an HMM to define foraging and commuting.

# load libaries
```{r setup, include=FALSE}
library(pacman)
# devtools::install_github("ABoVE-AotM/above")
p_load(above, move, maptools,
       dplyr, leaflet, lubridate, maps, mapdata, marcher, rgdal, 
       gfcanalysis,snow,patchwork,
       raster,rlist,PBSmapping, 
       rnaturalearth, rnaturalearthdata, sp, momentuHMM,
       tidyverse, magrittr)

source("../../../movebank_login.R")

proj.ll <- CRS('+proj=longlat +datum=WGS84 +no_defs')
```

```{r}
# fractional tree cover
data_folder <- '../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data'

# aoi <- readOGR(system.file('extdata', package='gfcanalysis'), 'ZOI_NAK_2012')

x <- c(-82.59858974938628,-82.03210720544097, -82.03210720544097,-82.59858974938628)
y <- c(9.125631468384787,9.125631468384787,9.510498999474096,9.510498999474096)
xy <- cbind(x,y)
p <- Polygon(xy)
ps <- Polygons(list(p),1)
sps <- SpatialPolygons(list(ps))
# plot(sps)
proj4string(sps) = CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

aoi <- sps

# # Calculate the google server URLs for the tiles needed to cover the AOI
# tiles <- calc_gfc_tiles(aoi)
# 
# # Check to see if these tiles are already present locally, and download them if 
# # they are not.
# download_tiles(tiles, data_folder, )
# 
# # Extract the GFC data for this AOI from the downloaded GFC tiles, mosaicing 
# # multiple tiles as necessary (if needed to cover the AOI), and saving  the 
# # output data to a GeoTIFF (can also save in ENVI format, Erdas format, etc.).
# gfc_data <- extract_gfc(aoi, data_folder, filename='gfc_Bocas_extract.tif', overwrite = TRUE)
# 
# plot(gfc_data)
# 
# tgfc <- threshold_gfc(gfc_data)
# 
# gfc_stack <- annual_stack(tgfc)
# 
# plot(gfc_stack[[16]])
# 
# save(gfc_data, gfc_stack, tgfc, file = "../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/forestcoverBocas.rdata")
load("../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/forestcoverBocas.rdata")
```


# read movebank data
```{r}
# phast <- getMovebankData(study="Greater spear-nosed bat (Phyllostomus hastatus) in Bocas del Toro 2021-2022", login=login, removeDuplicatedTimestamps = TRUE)
# sensors <- getMovebankSensorsAttributes(study="Greater spear-nosed bat (Phyllostomus hastatus) in Bocas del Toro 2021-2022", login=login)
# 
# save(phast, sensors, file = "../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/phastmove.rdata")
load("../../../../Dropbox/MPI/Phyllostomus/Fieldwork/Data/phastmove.rdata")
#phast_gps <- getMovebankData(study="Greater spear-nosed bat (Phyllostomus hastatus) in Bocas del Toro 2021-2022", login=login, removeDuplicatedTimestamps = TRUE, sensorID = "GPS")
```

# remove outlier
```{r}
phast <- phast[phast$location_long > -90,]
plot(phast)
```


```{r}
summary(phast)
sensors
namesIndiv(phast)
move.df <- as.data.frame(phast)
```
# number of individuals
```{r}
length(unique(move.df$tag_id))
sort(table(move.df$tag_id))
```

# spatial extent of the study
```{r}
range(move.df$location_long)
range(move.df$location_lat)
xlim <- c(-83, -82.2)
ylim <- c(9.3, 9.7)
```
# plot data
```{r}
gfc_data 
tree <- crop(gfc_data[[1]], extent(c(xlim, ylim)))

tree.df <- data.frame(x=coordinates(tree)[,1], y=coordinates(tree)[,2], fcover=values(tree))

ggplot(move.df, aes(x=location_long, y=location_lat)) +
  geom_raster(data=tree.df, aes(x=x, y=y, fill=fcover)) +
  scale_fill_viridis_c(name='Fractional tree cover', limits=c(0,100), option='E', alpha=0.7) +
  geom_point(aes(colour=factor(tag_id)), size=0.5, show.legend=F)+ 
  scale_colour_viridis_d(name='Individual', option='A') +
  theme(legend.position='bottom') + coord_equal() +
  labs(x='Longitude', y='Latitude')
```

```{r}
rm(tree.df, gfc_data, gfc_stack,tgfc); gc()
```

```{r}
ggplot(move.df, aes(x=ground_speed)) +
  geom_histogram(fill='black', colour='black', binwidth=2)+xlim(c(-5,60))

# move.df$speed <- phast %>% speed %>% unlist
plot(speed(phast[[1]]))
phast %>% speed %>% unlist %>% hist(breaks = 100)

phast %>% distance %>% unlist %>% hist(breaks = 50000, xlim = c(0,5000))
```

```{r}
p <- SpatialPoints(move.df[,c('location_long', 'location_lat')], proj4string=CRS('+proj=longlat +datum=WGS84'))

move.df$fcover <- extract(tree, p) # using nearest-neighbour method

ggplot(move.df, aes(x=fcover)) +
  geom_histogram(fill='white', colour='black', binwidth=5) +
  facet_wrap(~factor(ground_speed>2, labels=c('Ground speed < 2m/s', 'Ground speed > 2m/s')), ncol=1)
```
# Adding sun angle and solar time
```{r}
# compute time relative to solar noon for each location
move.df$solar.time <- unlist(lapply(1:nrow(move.df), function(j){
  noon <- solarnoon(p[j,], move.df$timestamp[j], POSIXct.out=TRUE)$time
  tod <- as.numeric(difftime(move.df$timestamp[j], noon, units='hours'))
  return(tod)
}))

# shift solar time to be all-positive, from noon to noon
move.df$solar.time <- (move.df$solar.time+24)%%24

# compute solar elevation
move.df$solar.pos <- unlist(lapply(1:nrow(move.df), function(j){
  pos <- solarpos(p[j,], move.df$timestamp[j])
  return(pos[,2])
}))


twilight <- data.frame('name'= c('Dawn/Dusk', 'Civil Twilight', 'Nautical Twilight', 'Astronomical Twilight'),
                       'solar.pos'=c(0, -6, -12, -18), stringsAsFactors=F)
twilight$name <- factor(twilight$name, levels=c('Dawn/Dusk', 'Civil Twilight', 'Nautical Twilight', 'Astronomical Twilight'))

ggplot(move.df, aes(x=solar.pos)) + 
  geom_histogram(fill='white', colour='black', binwidth=3) +
  geom_vline(data=twilight, aes(xintercept=solar.pos, colour=name), size=1.5) +
  scale_colour_viridis_d(name='', direction=-1)
```
```{r}
# no sampling during daytime
p1 <- ggplot(move.df, aes(x=solar.time)) + geom_histogram(fill='white', colour='black', binwidth=1) + 
  scale_x_continuous(breaks=seq(0,23,2), limits=c(0,23)) +
  theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
p2 <- ggplot(move.df, aes(x=ground_speed)) +
  scale_x_continuous(breaks=seq(0,25,5)) +
  geom_histogram(fill='white', colour='black', binwidth=1.5) + 
  coord_flip() + theme(axis.text.y=element_blank(), axis.title.y=element_blank(), 
                       axis.ticks.y=element_blank(), axis.text.x=element_text(angle=90))
p3 <- ggplot(move.df, aes(x=solar.time, y=ground_speed, colour=fcover)) +
  geom_point(size=0.7) + scale_colour_viridis_c() + 
  scale_x_continuous(breaks=seq(0,23,2), limits=c(0,23)) +
  scale_y_continuous(breaks=seq(0,25,5)) + theme(legend.position='bottom')

p1 + plot_spacer() + p3 + p2 + plot_layout(ncol=2, widths=c(0.8, 0.2), heights=c(0.3, 0.7))
```


# acc data is strange for vesper bats
```{r}
phast$acceleration_raw_x %>% plot
acc_idx <- which(!is.na(phast$acceleration_raw_x))
phast[acc_idx,] %>% plot
summary(phast[acc_idx,])
```


```{r}
layout(c(1,2,3))
plot(phast$acceleration_raw_x[acc_idx], type = "l")
plot(phast$acceleration_raw_y[acc_idx], type = "l")
plot(phast$acceleration_raw_z[acc_idx], type = "l")
```

```{r}



```



```{r}
p_sum <- data.frame()
j = 1
for(j in 1:length(unique(phast$tag_id))){
  indiv <- phast[[j]]
  plot(indiv)
  scan_track(x = indiv$location_long, y = indiv$location_lat, time = indiv$timestamp, 
             cex = indiv$ground_speed*2/max(indiv$ground_speed))  
  
  # identify number of foraging days
  dates <- indiv$timestamp %>% ymd_hms %>% date %>% unique 
  dates
  
  # departure, return, duration of flights
  ind_sum <- data.frame(tag_id = indiv$tag_id[1], date = dates, 
                        start = ymd_hms("2000-01-01 00:00:00"), 
                        end = ymd_hms("2000-01-01 00:00:00"))

  for(i in 1:length(dates)){
    d <- indiv[date(indiv$timestamp) == dates[i],]
    plot(d)
    ind_sum$start[i] <- d$timestamp[1]
    ind_sum$end[i] <- d$timestamp[nrow(d)]
    ind_sum$distance[i] <- sum(distance(d))
    
    ind_sum$max_speed[i] <- max(speed(d))
  }
  p_sum <- rbind(p_sum, ind_sum)
}

```


# identify foraging locations

## HMM
```{r}

```


