---
title: "BORIS_ACC_WildBats"
output: html_document
date: 2023-08-01
---

Code for Johannes to summarize the behavioral categories of wild Phyllostomus 
hastatus estimated from acceleration models.

# load libraries
```{r}
library(pacman)
p_load(tidyverse, data.table, lubridate, vcd, reshape2, glmmTMB, report)
```

# load data
```{r}
# files <- list.files("./../../../Dropbox/MPI/Phyllostomus/BORIS/rf_bats/", full.names = TRUE)
# 
# df <- data.table()
# i = 1
# for(i in 1:length(files)){
#   d <- fread(files[i])
#   df <- rbind(df, d)
# }
# 
# df$date <- date(df$time-12*3600)
# df$hour <- hour(df$time-12*3600)
# df$behavior[df$behavior == "resting"] <- df$rf_behavior[df$behavior == "resting"]
# # table(df$behavior)
# # unique(df$date)
# df %>% reframe(sleeping = length(which(behavior == "sleeping"))/n(),
#                climbing = length(which(behavior == "climbing"))/n(),
#                grooming = length(which(behavior == "grooming"))/n(),
#                foraging = length(which(behavior == "foraging" | 
#                                          behavior == "flying"))/n(),
#                commuting = length(which(behavior == "commuting"))/n(),
#                ODBA = sum(odba, na.rm = TRUE),
#                VeDBA = sum(vedba, na.rm = TRUE),
#                count = n(),
#                .by = c(date, bat)) -> df_sum
# # remove days with missing data or tag fell off
# df_sum <- df_sum[df_sum$count > 30000 & df_sum$ODBA > 100000 & df_sum$climbing < 0.05,]

load("../../../../Dropbox/MPI/Dechmann_Lab/Johannes Bernecker/wildbats.robj")
```

```{r}
df_sum_mlt <- melt(df_sum, c("bat", "date", "count", "ODBA", "VeDBA"))
ggplot(df_sum_mlt, aes(x = date, y = value*100, col = variable))+
  geom_point()+
  ylab("%")+
  theme_bw()+facet_wrap(~bat)

ggplot(df_sum_mlt, aes(x = variable, y = value*100))+
  geom_boxplot()+ylab("%")+xlab("")+theme_bw()
```
```{r}
df_sum %>% reframe(sleep = paste0("mean:", round(mean(sleeping*100), 1), ", sd: ", round(sd(sleeping*100),1)),
                   climb = paste0("mean:", round(mean(climbing*100), 1), ", sd: ", round(sd(climbing*100),1)),
                   groom = paste0("mean:", round(mean(grooming*100), 1), ", sd: ", round(sd(grooming*100),1)),
                   forage = paste0("mean:", round(mean((foraging)*100), 1), ", sd: ", round(sd((foraging)*100),1)),
                   commute = paste0("mean:", round(mean(commuting*100), 1), ", sd: ", round(sd(commuting*100),1))) -> behav_percent

data.frame(behavior = behav_percent %>% names, mean_sd = as.character(behav_percent[1,]))
```

# what time do bats do each behavior?
```{r}

df %>% reframe(sleeping = length(which(behavior == "sleeping"))/n(),
               climbing = length(which(behavior == "climbing"))/n(),
               grooming = length(which(behavior == "grooming"))/n(),
               flying = length(which(behavior == "flying"))/n(),
               foraging = length(which(behavior == "foraging"))/n(),
               commuting = length(which(behavior == "commuting"))/n(),
               ODBA = sum(odba, na.rm = TRUE),
               VeDBA = sum(vedba, na.rm = TRUE),
               count = n(),
               .by = c(date, hour, bat)) -> df_hr_sum

df_hr_sum <- df_hr_sum[df_hr_sum$count > 1000,]
```

# plot the activity percentage for each hour
```{r}
df_hr_sum_mlt <- melt(df_hr_sum, c("bat", "hour", "date", "count", "ODBA", "VeDBA"))
ggplot(df_hr_sum_mlt, aes(x = hour, y = value*100, col = variable))+
  geom_point()
```

# when is each behavior most common?
```{r}
df_hr_sum %>% reframe(sleep = mean(sleeping), 
                      climb = mean(climbing),
                      groom = mean(grooming),
                      foraging = mean(flying+foraging),
                      commuting = mean(commuting),
                      .by = hour) -> hr_sum
hr_sum_mlt <- melt(hr_sum, "hour")
ggplot(hr_sum_mlt, aes(x = hour, y = value, col = variable))+
  geom_point()+ylab("%")+theme_bw()
```

# What relationships would you have expected for ODBA and VeDBA to have with each behavior?
Climbing and flying should create higher VeDBA, so an increase in that alone would shoud have a positive relationship. Why don't we see that relationship? Sleeping means you aren't moving at all, so, in isolation, more sleep should mean lower VeDBA. 

```{r}
ggplot(df_sum_mlt, aes(x = value, y = scale(VeDBA), col = variable))+
  geom_point()+
  # geom_smooth(method = "lm")+
  xlab("%") + ylab("VeDBA")+
  facet_wrap(~variable)+theme_bw()
```

# summarise daily behavior
check that covariates are not correlated
sleeping is correlated with grooming, so we can only include sleeping in the model
```{r}
psych::pairs.panels(df_sum)
```

# model these results
```{r}
fit_sleeping <- lm(scale(VeDBA) ~ sleeping+foraging+commuting+climbing, data = df_sum)
summary(fit_sleeping)
report(fit_sleeping)
report(fit_sleeping) %>% as.data.frame()
```
These results suggest that the more you sleep the lower your VeDBA, which I think is the opposite of your prediction. My guess is that since sleep has super low VeDBA, it is simply a time effect where more time not moving will inevitably lead to lower total movement. Still fun to test a hypothesis!

# save data
```{r}
save(df_sum, file = "../../../../Dropbox/MPI/Dechmann_Lab/Johannes Bernecker/wildbats.robj")
```



